Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
Wording of "acknowledgements"
markups -> markup

To specify examples/properties for users, we propose to add two new markups to Haddock and to use {\tt doctest} integrated with QuickCheck. To describe examples/properties for developers, we propose to use \hspec{} also integrated with QuickCheck.

@@

We are grateful to David Waern, 
one of the Haddock maintainers, 
for reviewing two new markups to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that 
properties which do not have parameters are tested just once.

>>>>

To specify examples/properties for users, we propose to add two new markup to Haddock and to use {\tt doctest} integrated with QuickCheck. To describe examples/properties for developers, we propose to use \hspec{} also integrated with QuickCheck.

@@

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that 
properties which do not have parameters are tested just once.
